---
title: "LRP"
author: "Keith Lewis"
date: "4/12/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## SSB
Definition: a level of SSB at which R starts to decline relative to sume upper range where R is assumed to be constant (on average)

Pros
- ICES recommended approach when possible
- Uses change-point regression or expert judgement
- Sound theoretical/analytical approach

Cons
- Assumes R is more affected by SSB than environmental factors


Assumes
- The relationship between SSB and R is known.

- See Hague et al. 2007 and ICES 2005
Show slide of relationship


## Bloss
Definition: SSB level below which there is no historical record of recruitment
pros/cons
Used when no SSB/R relationship

Pros
- Can be used in place of SSB/R derived Blim

Cons
- Arbitrary
- Environmental conditions at historically low SSB levles may have been favourable for R by coincidence

## Bpa
Still need SSB

## ICES Type I (Brecover)
lowest recorded biomass that produced high recruitment
- Used for 3Ps Haddock and Barents Sea capelin
pros/cons


```{r cars, echo = TRUE}
summary(cars)
```

## Multivariate - Bloss??

Pros
- Several measures - increased evidence that "something is wrong"
- 

Cons
- a new approach
```{r pressure}
plot(pressure)
```